Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
delete philopatry comment
question 1

Forage limitation may be the ultimate explanation for caribou swimming between
oceanic islands, but cannot fully explain the variation we observed. Several
questions remain:

1) How does the energetic cost or risk of swimming differ from walking across
sea ice? How many individuals were observed travelling between islands during
the winter, relative to the 12 swimmers?

@@

Oceanic swimming is relatively common among a minority of marked caribou. Of the
three collared individuals that swam the most, two were collared on Western
Indian Island and the third was collared on Fogo Island. Inter-island distances
between Western and Eastern Indian Islands, and the smaller islands around them,
are shorter than those between Fogo Island and others (Figure 2). It is possible
that caribou display natal philopatry [e.g. @Larue2018] to some of the smaller
islands and thus are more likely to swim between them more frequently than
animals that were born, or spend most of their time, on Fogo Island.

>>>>

Forage limitation may be the ultimate explanation for caribou swimming between
oceanic islands, but a number of proximate mechanisms remain untested. Our
observations of caribou swimming in the ocean to five questions for future
research:

1) How does the energetic cost or risk of swimming differ from walking on sea
ice? The cost of swimming may be lower than the risk of falling through sea ice
and drowning, so what proportion of inter-island movements are swimming events
compared to walking on ice? Although we are unable to

@@

Oceanic swimming is relatively common among a minority of marked caribou. Of the
three collared individuals that swam the most, two were collared on Western
Indian Island and the third was collared on Fogo Island. Inter-island distances
between Western and Eastern Indian Islands, and the smaller islands around them,
are shorter than those between Fogo Island and others (Figure 2).
